### 2022-12-02 proof.tex
details

\begin{theorem}
{\sc $k$-resilience} is decidable for effective WSTS with strong monotony.
\end{theorem}

Assume  $(S, \rightarrow, \leq)$ is a SWSTS with upward compatibility, $J$ is a decidable downward-closed subset of $S$, and $I$ is an upward-closed set with a given basis.

@@

@@

Formally, let us show that $\uparrow post(\uparrow post^*(s)) \subseteq \uparrow post^*(s)$.
Let $b \in \uparrow post(\uparrow post^*(s))$ 
there exists $a', a, b$ such that
$s \rightarrow^* a'$,
$a' \leq a$,
$a \rightarrow b'$,
and
$b' \leq b$.
% By monotonicity, there exists b'' ≥ b' such that a → b'' . Therefore, x → ∗ b'' and b' ≥ b, hence b ∈ ↓ Post ∗ (x).
\textcolor{red}{By downward compatibility 
there exists $b'' \leq b'$ such that $a \rightarrow b'' $. Therefore, $x \rightarrow^* b''$ and $b' \geq b$, hence $b \in \downarrow post^*(x)$.}
\alain{où est cette hypothèse downward compatibility  ?}
\item Procedure 2 computes
 $post^{\leq n}(s) \cap J$
 until it finds an element not in $ I^k$.

@@

\begin{theorem}
{\sc resilience} is decidable for WSTS with strong monotony.
\end{theorem}

@@

>>>>

@@

This result is not in xxx and don't use the problematic hypothsis on $post^*$.

\begin{theorem}
{\sc $k$-resilience} is decidable for effective WSTS with downward/upward compatibility.
%	with strong monotony.
\end{theorem}

Assume  $(S, \rightarrow, \leq)$ is a WSTS with downward/upward compatibility, $J$ is a decidable downward-closed subset of $S$, and $I$ is an upward-closed set with a given basis.

@@

Formally, let us show that $\uparrow post(\uparrow post^*(s)) \subseteq \uparrow post^*(s)$.
Let $b \in \uparrow post(\uparrow post^*(s))$ 
there exists $a', a, b$ such that
$s \rightarrow^* a'$,
$a' \leq a$,
$a \rightarrow b'$,
and
$b' \leq b$.
% By monotonicity, there exists b'' ≥ b' such that a → b'' . Therefore, x → ∗ b'' and b' ≥ b, hence b ∈ ↓ Post ∗ (x).
\textcolor{red}{By downward compatibility 
there exists $b'' \leq b'$ such that $a \rightarrow b'' $. Therefore, $x \rightarrow^* b''$ and $b' \geq b$, hence $b \in \downarrow post^*(x)$.}
%\alain{où est cette hypothèse downward compatibility  ?}
\item Procedure 2 computes
 $post^{\leq n}(s) \cap J$
 until it finds an element not in $ I^k$.

@@

\begin{theorem}
{\sc resilience} is decidable for WSTS with downward/upward compatibility.
\end{theorem}

@@

{\sc resilience} is decidable for WSTS with strong upward compatibility and k-resilience.

jouer avec les hypothèses downward/upward compatibility

\begin{proof}
totot
\end{proof}
